Adapting to Quasi-Periodic and Secular Changes of Climate Risk

### 2018-03-03 writeup/main.tex
Dave updated results, discussion, and summary

To do this we generate 1000 sequences of streamflow for each combination of $M$, $N$, and generative process.
The parameters for the NINO3 model are given in \cref{tab:nino-stationary} and for the Markov model in \cref{tab:nino-stationary}.
We use a threshold $Q_T = \SI{5000}{units}$.
We then fit each estimation model to each sequence and draw 2000 estimates of future streamflow from the fitted model.
These are then used to determine $\hat{p}_T$, allowing calculation of the expected bias and variance in its estimation for each combination of $M$, $N$, generative model, and estimating model.

@@

\Cref{fig:stationary-bias} shows that in general, bias is quite similar across generative models but varies substantially between the models used for estimation.
The HMM and LN2 Stationary models have no time term, and so their bias is independent of $M$.
In general both of these models have very low bias, though the LN2 Stationary model tends to over-estimate the probability of flooding for very short $N$, unsurprising since the true distribution of streamflow is bimodal for both generating functions. 
The LN2 trend model registers a non-trivial probability of a positive time trend, particularly for short $N$, leading to large bias in estimation.
For very long $M$ the bias is higher, as estimated probability of exceeding the threshold is exceeded.
\begin{figure}[ht]
  \includegraphics[width=\textwidth]{bias_stationary.pdf}
  \caption{The estimation bias for 1000 sequences generated by each of two stationary generating functions (row) and fit by each of three fitting functions (columns) as a function of $M$ and $N$.\label{fig:stationary-bias}}
\end{figure}

Analysis of the variance, in these estimates, shown in \cref{fig:stationary-variance} as the log standard deviation, is similar.
As suggested in the bias plots, the HMM and LN2 Stationary models have very low variance of their estimates.
The LN2 Trend model has much higher variance in estimates, particularly for short $N$ or short $M$.
\begin{figure}[ht]
  \includegraphics[width=\textwidth]{variance_stationary.pdf}
  \caption{The estimation variance for 1000 sequences generated by each of two stationary generating functions (row) and fit by each of three fitting functions (columns) as a function of $M$ and $N$.\label{fig:stationary-variance}}
\end{figure}

@@

\emph{Please comment: should this be part of our paper?}

@@

\section{Discussion}

>>>>

To do this we generate 1000 sequences of streamflow for each combination of $M$, $N$, and generative process.
The parameters for the NINO3 and Markov models are given in \cref{tab:nino-stationary}.
We use a threshold $Q_T = \SI{5000}{units}$.
We then fit each estimation model to each sequence and draw 2000 estimates of future streamflow from the fitted model.
These are then used to determine $\hat{p}_T$, allowing calculation of the expected bias and variance in its estimation for each combination of $M$, $N$, generative model, and estimating model.

@@

\Cref{fig:stationary-bias}\footnote{It's more intuitive for me if the M axis is increasing upwards, but perhaps there is a reason for your orientation that I am not considering} shows that in general, bias is quite similar across generative models but varies substantially between the models used for estimation.
The HMM and LN2 Stationary models have no time term, and so their bias is independent of $M$.
In general both of these models have very low bias, though the LN2 Stationary model tends to over-estimate the probability of flooding for very short $N$, unsurprising since the true distribution of streamflow is bimodal for both generating functions. 
The LN2 trend model registers a non-trivial probability of a positive time trend, particularly for short $N$, leading to large bias in estimation.
For very long $M$ the bias is higher, as estimated probability of exceeding the threshold is exceeded.
\begin{figure}[ht]
  \includegraphics[width=\textwidth]{bias_stationary.pdf}
  \caption{The estimation bias for 1000 sequences generated by each of two stationary generating functions (row) and fit by each of three fitting functions (columns) as a function of $M$ and $N$.\label{fig:stationary-bias}}
\end{figure}

The variance estimates show similar patterns to those of the bias and are shown in \cref{fig:stationary-variance} as the log standard deviation.
As suggested in the bias plots, the HMM and LN2 Stationary models have very low variance of their estimates.
The LN2 Trend model has much higher variance in estimates, particularly for short $N$ and long $M$.
\begin{figure}[ht]
  \includegraphics[width=\textwidth]{variance_stationary.pdf}
  \caption{The estimation variance for 1000 sequences generated by each of two stationary generating functions (row) and fit by each of three fitting functions (columns) as a function of $M$ and $N$.\label{fig:stationary-variance}}
\end{figure}

@@

\emph{Please comment: should this be part of our paper?}\footnote{I vote yes to include this, since I think it nails the "so-what?" part}

@@

\section{Discussion}\footnote{Not doing much editing from here on yet, since I think it will depend a bit on a more finalized version of the above sections. The beginning of the discussion does read as introductory material to me -- likely a case study in between sections 3 and 5 will help ease the reader from the discussion of bias and variance for N and M (without much context) in section 3 into the very applied considerations discussed at the beginning of section 5. Still I do think that the discussion could use some re-focusing. Also, adding some context in the results section will help to set up a productive discussion I think.}
